---
title: "PACTS Study"

subtitle: "Analysis of trial results"

author: |
  | Peter MacPherson
  |
  | Liverpool School of Tropical Medicine, Liverpool, UK
  | Malawi-Liverpool-Wellcome Clinical Research Programme, Blantyre, Malawi
  |

date: | 
  | `r format(Sys.time(), "%B %d, %Y")`
  |
  | Table of Contents:
output: 
  html_document:
    theme: cosmo
    toc: true
---

<br>

## 1. Backgound

Analysis of the PACTS Study trial data.

<br>

## 2. Set-up

Load all required packages for analysis.

```{r setup, message=FALSE, comment=NA, warning=FALSE}
library(tidyverse)    #for data manipulation
library(pmthemes)     #for ggplot themes
library(knitr)        #for tables
library(here)         #for file nagivation
library(arsenal)      #for tables of baseline characteristics
library(rms)          #for regression modelling
library(janitor)      #for tables

```

<br>

## 3. Table 1: Baseline characteristics of participants and household members

These data are taken from table `pacts03_indexbase`.

```{r import}
data("index_baseline", package="PACTSstudy")

table1 <- tableby(group ~ sex + age + marital + educ + employ +
                  hiv + art + tbtype + hh_size + hh_children +
                  hh_u5 + head_age + head_sex + hh_prevtb +wealth_quintile,  
                  data = index_baseline, test=FALSE, 
                  numeric.stats=c("medianrange"), digits=1)

kable(summary(table1))


```

<br>

## 4. Table 2: Baseline characteristics of household contacts

These data are taken from tables `pacts04A_hhTBscreen1` and `pacts04A_hhTBscreen2`.

```{r}
data("contacts_threemonths", package="PACTSstudy")

table2 <- tableby(group ~ p05age + contact_agegroup + contact_sex +
                  contact_educ,
                  data = contacts_threemonths, test=FALSE,
                  numeric.stats=c("medianrange"), digits=1)

kable(summary(table2))


```

<br>

## 5. Primary outcome 1: Proportion of household contacts diagnosed with TB

i.e. with microbiologically confirmed TB, or taking TB treatment.

First univariate model. Note that we adjust confidence intervals for household clustering by using the sandwich estimator.

```{r}
data("contacts_threemonths", package="PACTSstudy")

contacts_threemonths %>%
  tabyl(m3_tb_out, group) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

up1 <- lrm(m3_tb_out ~ group, x=T, y=T, data=contacts_threemonths)
up1
up1<-robcov(up1, cluster=contacts_threemonths$id)
kable(cbind((exp(up1$coefficients)), exp(confint.default(up1))), digits=2)
```

Now construct a multivariable model. We adjust for trial arm, wealth quintile, and TB type of index case.

Model internal validation is done using 1000 bootstrap replications. Note the over-optimism that this will externally validate by inspecting Somer's Dxy statistic.

```{r}
#Multivariable model
mp1 <- lrm(m3_tb_out ~ group + wealth_quintile + tbtype, x=T, y=T, data=contacts_threemonths)
mp1
mp1<-robcov(mp1, cluster=contacts_threemonths$id)
kable(cbind((exp(mp1$coefficients)), exp(confint.default(mp1))), digits = 2)

#validate the model
validate(mp1, B=1000)

cmp1 <- calibrate(mp1, B=1000)

plot(cmp1)


```

<br>

## 6. Primary outcome 2: Proportion of Under 5s who initiated IPT.

First univariate model. Note that we adjust confidence intervals for household clustering by using the sandwich estimator.

```{r}

data("under5s_3m", package="PACTSstudy")

under5s_3m %>%
  tabyl(iptrx, group) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

up2 <- lrm(iptrx ~ group, x=T, y=T, data=under5s_3m)
up2
up2<-robcov(up2, cluster=under5s_3m$id)
kable(cbind((exp(up2$coefficients)), exp(confint.default(up2))), digits=2)
```

Now construct a multivariable model. We adjust for trial arm, wealth quintile, and  TB type of index case.

Model internal validation is done using 1000 bootstrap replications. Note the over-optimism that this will externally validate by inspecting Somer's Dxy statistic.

```{r}
mp2 <- lrm(iptrx ~ group + wealth_quintile + tbtype, x=T, y=T, data=under5s_3m)
mp2
mp2<-robcov(mp2, cluster=under5s_3m$id)
kable(cbind((exp(mp2$coefficients)), exp(confint.default(mp2))), digits = 2)

#validate the model
validate(mp2, B=1000)

cmp2 <- calibrate(mp2, B=1000)

plot(cmp2)


```

<br>

## 7. Secondary outcome 1: Proportion of Under 5s who completed IPT within 9 months.

First univariate model. Note that we adjust confidence intervals for household clustering by using the sandwich estimator.

```{r}
data("nine_month", package="PACTSstudy")

nine_month %>%
  tabyl(ipt9comp2, arm2) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

us1 <- lrm(ipt9comp2 ~ arm2, x=T, y=T, data=nine_month)
us1
us1<-robcov(us1, cluster=nine_month$id)
kable(cbind((exp(us1$coefficients)), exp(confint.default(us1))), digits=2)

```

Now construct a multivariable model. We adjust for trial arm, wealth quintile, and TB type of index case.

Model internal validation is done using 1000 bootstrap replications. Note the over-optimism that this will externally validate by inspecting Somer's Dxy statistic.

```{r}
#Multivariable model
ms1 <- lrm(ipt9comp2 ~ arm2 + wealth_quintile + smear, x=T, y=T, data=nine_month)
ms1
ms1<-robcov(ms1, cluster=nine_month$id)
kable(cbind((exp(ms1$coefficients)), exp(confint.default(ms1))), digits = 2)

#validate the model
validate(ms1, B=1000)

cms1 <- calibrate(ms1, B=1000)

plot(cms1)


```

<br>

## 8. Secondary outcome 2: Proportion of household contacts with TB symptoms at 3 months.

First univariate model. Note that we adjust confidence intervals for household clustering by using the sandwich estimator.

```{r}
data("contacts_threemonths", package="PACTSstudy")

contacts_threemonths %>%
  tabyl(sx_3m, group) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

us2 <- lrm(sx_3m ~ group, x=T, y=T, data=contacts_threemonths)
us2
us2<-robcov(us2, cluster=contacts_threemonths$id)
kable(cbind((exp(us2$coefficients)), exp(confint.default(us2))), digits=2)
```

Now construct a multivariable model. We adjust for trial arm, age (restricted cubic spline with 4 knots), sex, wealth quintile, TB type of index case, and HIV.

Model internal validation is done using 1000 bootstrap replications. Note the over-optimism that this will externally validate by inspecting Somer's Dxy statistic.

```{r}
#Multivariable model
ms2 <- lrm(sx_3m ~ group + wealth_quintile + tbtype, x=T, y=T, data=contacts_threemonths)
ms2
ms2<-robcov(ms2, cluster=contacts_threemonths$id)
kable(cbind((exp(ms2$coefficients)), exp(confint.default(ms2))), digits = 2)

#validate the model
validate(ms2, B=1000)

cms2 <- calibrate(ms2, B=1000)

plot(cms2)


```

<br>

## 9. Secondary outcome 3: Proportion of household contacts with micro-confirmed TB at 3 months.

First univariate model. Note that we adjust confidence intervals for household clustering by using the sandwich estimator.

```{r}

data("contacts_threemonths", package="PACTSstudy")

contacts_threemonths %>%
  tabyl(s3_micro_confirmed, group) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

us3 <- lrm(s3_micro_confirmed ~ group, x=T, y=T, data=contacts_threemonths)
us3
us3<-robcov(us3, cluster=contacts_threemonths$id)
kable(cbind((exp(us3$coefficients)), exp(confint.default(us3))), digits=2)
```


Because there are so few events (n=3 in total), I don't think it makes sense to do multivariable analysis). But here we go anyways...

Model internal validation is done using 1000 bootstrap replications. Note the over-optimism that this will externally validate by inspecting Somer's Dxy statistic.

```{r}
#Multivariable model
ms3 <- lrm(s3_micro_confirmed ~ group + wealth_quintile + tbtype, x=T, y=T, data=contacts_threemonths)
ms3
ms3<-robcov(ms3, cluster=contacts_threemonths$id)
kable(cbind((exp(ms3$coefficients)), exp(confint.default(ms3))), digits = 2)

#validate the model
validate(ms3, B=1000)

cms3 <- calibrate(ms3, B=1000)

plot(cms3)


```

<br>

## 10. Secondary outcome 4: Proportion of households where at least one household contact was investigated by either "sputum tests", or chest x-ray.


```{r}

data("household", package="PACTSstudy")

household <- household %>%
  mutate(arm2 = case_when(group=="PACTS" ~ "Intervention_PACTS",
                          group=="SOC" ~ "Control_SOC"))

household %>%
  tabyl(any_screen3m, arm2) %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable()

set.seed(42)

us4 <- lrm(any_screen3m ~ arm2, x=T, y=T, data=household)
us4
kable(cbind((exp(us4$coefficients)), exp(confint.default(us4))), digits=2)


ms4 <- lrm(any_screen3m ~ arm2 + wealth_quintile + tbtype, x=T, y=T, data=household)
ms4
kable(cbind((exp(ms4$coefficients)), exp(confint.default(ms4))), digits=2)

```




<br>

## 11. Reproducibility

This reproduction of the analysis was run by: 

```{r sysinfo, echo=FALSE, message=FALSE, comment=NA, warning=FALSE}

sysinfo <- Sys.info()

sysinfo <- data.frame(keyName=names(sysinfo), value=sysinfo, row.names=NULL)

sysinfo %>% kable()
```

Analysis was run at **`r Sys.time()`**, and using the following Session Info:

```{r sessioninfo, echo=FALSE, results='markdown', message=FALSE, comment=NA, warning=FALSE}
sessionInfo()
```
