---
title: "PACTS Study"

subtitle: "Analysis of trial results"

author: |
  | Peter MacPherson
  |
  | Liverpool School of Tropical Medicine, Liverpool, UK
  | Malawi-Liverpool-Wellcome Clinical Research Programme, Blantyre, Malawi
  |

date: | 
  | `r format(Sys.time(), "%B %d, %Y")`
  |
  | Table of Contents:
output: 
  html_document:
    theme: cosmo
    highlight: espresso
    toc: true
---

<br>

## 1. Backgound


<br>

## 2. Set-up

Load all required packages for analysis.

```{r setup, echo=FALSE, include=FALSE, message=FALSE, comment=NA, warning=FALSE}
library(tidyverse)    #for data manipulation
library(pmthemes)     #for ggplot themes
library(knitr)        #for tables
library(here)         #for file nagivation
library(arsenal)      #for tables of baseline characteristics

```

<br>

## 3. Table 1: Baseline characteristics of participants and household members

These data are taken from table `pacts03_indexbase`.

```{r import}
data("index_baseline", package="PACTSstudy")

table1 <- tableby(group ~ sex + age + marital + educ + employ +
                  hiv + art + tbtype + hh_size + hh_children +
                  hh_u5 + head_age + head_sex + hh_prevtb +wealth_quintile,  
                  data = index_baseline, test=FALSE, 
                  numeric.stats=c("medianrange"), digits=1)

kable(summary(table1))


```

<br>

## 3. Table 2: Baseline characteristics of household contacts

These data are taken from tables `pacts04A_hhTBscreen1` and `pacts04A_hhTBscreen2`.

```{r}
data("contacts_baseline", package="PACTSstudy")

table2 <- tableby(group ~ p05age + contact_agegroup + contact_sex + 
                  contact_educ,  
                  data = contacts_baseline, test=FALSE, 
                  numeric.stats=c("medianrange"), digits=1)

kable(summary(table2))


```


<br>

## X. Reproducibility

This reproduction of the analysis was run by: 

```{r sysinfo, echo=FALSE, message=FALSE, comment=NA, warning=FALSE}

sysinfo <- Sys.info()

sysinfo <- data.frame(keyName=names(sysinfo), value=sysinfo, row.names=NULL)

sysinfo %>% kable()
```

Analysis was run at **`r Sys.time()`**, and using the following Session Info:

```{r sessioninfo, echo=FALSE, results='markdown', message=FALSE, comment=NA, warning=FALSE}
sessionInfo()
```
